Finite-size scaling of free energy in the dimer model on a hexagonal domain

### 2019-06-14 AffineLieAlgebras/MQFT2018/paper.tex
Numeric check subsection in non-uniform section added

First sum in the expression \eqref{eq:46} can be expressed as follows. First, consider second
derivative of $\chi(z)$, separate an exponent and denote what is left by $\xi(z)$:
\begin{equation}
  \label{eq:48}
  \chi''(z)=e^{-z}\frac{e^{2 z} \left(z^2+4 e^z
   \left(z^2-1\right)+e^{2 z} \left(z^2-4
   z+2\right)+4
   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z)
\end{equation}
The sum is then rewritten
\begin{equation}
  \label{eq:49}
  \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}=
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}   
\end{equation}
The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}\right)\approx \ln
\varepsilon$,
the second term can approximated by the integral:
\begin{equation}
  \label{eq:50}
  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
\end{equation}
\begin{equation}
  \label{eq:51}
  \frac{\partial^{2} f}{\partial
  \varepsilon^{2}}\approx-\frac{1}{2(ab+bc+ca)}
\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right]
\end{equation}
Since we have logarithmic term in the second derivative, we have the behavior of free energy of the form
\begin{equation}
  \label{eq:26}
  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
\end{equation}
as expected in general in two-dimensional critical systems \cite{cardy1988finite}. Taking the
derivatives of such expression by $\varepsilon$, we get $f_{0}=f(0)$,
$f_{1}=\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}$,
$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+f_{3}$.

@@

\begin{equation}
  \label{eq:28}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:30}
  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12},
\end{equation}
and
\begin{equation}
  \label{eq:29}
  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
    \right].
\end{equation}

@@

\section{Numeric checks}
\label{sec:numeric-checks}
To check our result \eqref{eq:26} numerically, we first need to evaluate the integral in $f_{3}$.
The function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$ is smooth and but some care is required when taking the
limit $z\to 0$ numerically. Evaluating the integral numerically with Mathematica we get
\begin{equation}
  \label{eq:2}
  \int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.08084228607897521
\end{equation}

@@

Taking the derivatives of $f^{(0)}$ in $\varepsilon$ we get
\begin{multline}
  \label{eq:63}
  \left(\frac{d}{d\varepsilon}\right)^{2} f^{(0)}=\frac{1}{ab\varphi(b-a)} \sum_{n=1}^{\infty}
  \frac{1}{n^{3}}\left[
    \left.\tilde{\chi}''_{\varepsilon\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+
    2n\varphi(b-a)\left.\tilde{\chi}''_{z\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+\right.\\\left.
      n^{2}\left(\varphi(b-a)\right)^{2}\tilde{\chi}''_{zz}\left(n\varepsilon\varphi(b-a),\varepsilon\right)  \right]+
    \mathcal{O}(\varepsilon \ln \varepsilon)=\\
    =\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
      \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\tilde{\chi}''_{z\varepsilon}(0,0)\right]+
    \\
    +\frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon\varphi(b-a)\right)+\mathcal{O}(\varepsilon\ln \varepsilon),
\end{multline}
where
\begin{equation}
  \label{eq:64}
  \chi(z)=\frac{z^{2} e^{-z}}{\left(1-e^{-z}\right)^{2}}
\end{equation}
and
\begin{equation}
  \label{eq:65}
  H_{n}=\left(1-e^{-nb\varphi(b-a)}\right) \left(1-e^{-na\varphi(b-a)}\right)
\end{equation}

The last sum in the last line of the equation \eqref{eq:63} is the same as in the section
\ref{sec:gener-other-doma}, thus we can compute it:
\begin{equation}
  \label{eq:66}
  \frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon \varphi(b-a)\right)=
  \frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
    e^{-z}q(z) \dz+\chi''(0)\sum_{n=1}^{\infty}\frac{H_{n}-1}{n}\right),
\end{equation}
where $q(z)$ was defined in the equation

Now we need to consider other terms in the expression \eqref{eq:55}. For $f^{+}$ we have
\begin{equation}
  \label{eq:67}
  f^{+}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon\varphi(b-a)} \varepsilon
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)
\end{equation}
The sum over $j$ can be approximated by an integral using Euler-Maclaurin formula as
\begin{equation}
  \label{eq:68}
  \varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon) = \int_{0}^{a}\Psi^{+}_{n}(x) \dx -
  \frac{\varepsilon}{2}\left(\Psi^{+}_{n}(a)-\Psi^{+}_{n}(0)\right)+
  \frac{\varepsilon^{2}}{12}\left(\Psi^{+'}_{n}(a)-\Psi^{+}_{n}(0)\right)+
  \mathcal{O}\left(\varepsilon^{m}\Psi^{+(m-1)}_{n}\right)
\end{equation}
Since
\begin{equation}
  \label{eq:83}
\Psi_{n}(x)=e^{-nr'(0)x}\left(e^{-n\left(r(x)-xr'(0)\right)}-1\right)=e^{-nxr'(0)}\left(e^{-nx^{2}\zeta(x)}-1\right)  
\end{equation}
we see that $\Psi_{n}(0)=0$ and $\Psi_{n}'(0)=0$.
Than in the limit $n\to\infty$ we have
\begin{equation}
  \label{eq:69}
  \int_{0}^{c}\Psi_{n}(x)
  \dx \xrightarrow[n\to\infty]{}\int_{0}^{c}e^{-nxr'(0)}\left(-nx^{2}\zeta(x)+\dots\right)\sim \frac{1}{n^{2}}
\end{equation}
The derivatives of $\Psi$ behave as $\Psi_{n}^{(m)}(0)\sim n^{m-1}$, since the derivatives should
fall on the bracket in the expression \eqref{eq:83} for the value to be non-zero, and then extra
power of $x$ is produced, which in turn should be differentiated. So the contribution from
$\varepsilon^{m}\Psi_{n}^{(m-1)}(0)$ to $f^{+}$ gives us
\begin{equation}
  \label{eq:70}
  \sum_{n=1}^{\infty} \frac{1}{n} e^{-n\varepsilon\varphi(b-a)}
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} \varepsilon^{m+1}\Psi_{n}^{(m-1)}(0)\sim
  \sum_{n=1}^{\infty} \frac{1}{n^{4}} e^{-n\varepsilon\varphi(b-a)}
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} (\varepsilon n )^{m+1}
\end{equation}
For the second derivative in $\varepsilon$ we thus see that main contribution behaves as
$\sum_{n=1}\frac{1}{n^{2}}e^{-n\varepsilon\varphi(b-a)}
  (n\varepsilon)^{m+1}\xrightarrow[\varepsilon\to 0]{}0$
if $m\geq 3$. For the terms with $m=0,1,2$ we need to
take the limit $\varepsilon\to 0$. Doing so, we obtain
\begin{equation}
  \label{eq:71}
  \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}
  \left(\varepsilon\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon^{2} \Psi_{n}^{+}(a) +\varepsilon^{3}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}
\end{equation}
Note that $\frac{\varepsilon}{1-\exp(-n\varepsilon r'_{-}(0))}$ is analytic in $\varepsilon$. 
The derivative can be computed explicitly, but the expression is too long to present it here.

The contribution of $f^{-}$ is computed in exactly the same way:
\begin{equation}
  \label{eq:72}
  \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nar_{+}'(0)}}{1-e^{-n\varepsilon r_{+}'(0)}}
 \left(\varepsilon\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon^{2} \Psi_{n}^{-}(a) +\varepsilon^{3}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}
\end{equation}
At last, we need to consider $f^{\times}$. In this term we can just take a limit $\varepsilon\to 0$
and obtain
\begin{multline}
  \label{eq:73}
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}
    f^{\times}\right|_{\varepsilon=0}=\left.\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}
  \left(\frac{d}{d\varepsilon^{2}}\right)^{2}\left(\int_{0}^{b}\Psi^{-}_{n}(x)\dx
    -\frac{\varepsilon}{2}\Psi^{-}_{n}(b)+\frac{\varepsilon^{2}}{12}\Psi^{-'}_{n}(b)\right)\cdot\right.\\
\cdot\left.\left(\int_{0}^{a}\Psi^{+}_{n}(x)\dx-\frac{\varepsilon}{2}\Psi^{+}_{n}(a)+
    \frac{\varepsilon^{2}}{12}\Psi^{+}_{n}(a)\right)\right|_{\varepsilon=0} 
\end{multline}
Again, this expression is easily computed explicitly, but is too cumbersome to present it here. 
%%  
%%  If we assume that $\varphi(b-a)\neq 0$, we can again obtain function $\chi(z)$:
%%  \begin{multline}
%%    \label{eq:24}
%%     f=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{\chi\left(n\varepsilon\varphi(b-a)\right)}{n^{3}}\left(1-e^{-n\varepsilon
%%         \varphi(b-a)}\right)^{2}\frac{1}{\varphi^{2}(b-a)}\cdot\\
%%     \cdot\left(1+\sum_{i=1}^{N-1}
%%       e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
%%     \left(1+\sum_{j=1}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right)  
%%  \end{multline}
%%

@@

In further work we will show the connection of the expansion coefficients with the spectral
properties of Dirac operator on the non-frozen domain and study the universality of the presented
expressions by considering the model on more generic domain geometries with the non-uniform
Kasteleyn weighting with $q$ depending on the coordinate.

\section*{Acknowledgments}
\label{sec:acknowledgements}
I am grateful to professor Nikolai Reshetikhin for his guidance in this work. I thank Pavel Belov
for useful discussions and general support.

I thank the organizers and participants of the conference MQFT-2018 for the opportunity
to present our results and useful discussions.

>>>>

First sum in the expression \eqref{eq:46} can be expressed as follows. First, consider second
derivative of $\chi(z)$, separate an exponent and denote what is left by $\xi(z)$:
\begin{equation}
  \label{eq:48}
  \chi''(z)=e^{-z}\frac{e^{2 z} \left(z^2+4 e^z
   \left(z^2-1\right)+e^{2 z} \left(z^2-4
   z+2\right)+4
   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z)
\end{equation}
The sum is then rewritten
\begin{equation}
  \label{eq:49}
  \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}=
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}   
\end{equation}
The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}\right)\approx \ln
\varepsilon$. 
Denote by $Q(z)$ the difference of the function $\xi$ value in $z$ and zero, divided by z:
\begin{equation}
  \label{eq:85}
  Q(z)=\frac{\xi(z)-\xi(0)}{z}.
\end{equation}
The function $Q(z)$ is analytic in $z$.

Then the second term can approximated by the integral:
\begin{equation}
  \label{eq:50}
  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}Q(n\varepsilon)=\varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz=\int_{0}^{\infty}e^{-z}Q(z)\dz
\end{equation}
\begin{equation}
  \label{eq:51}
  \frac{\partial^{2} f}{\partial
  \varepsilon^{2}}\approx-\frac{1}{2(ab+bc+ca)}
\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right]
\end{equation}
Since we have logarithmic term in the second derivative, we have the behavior of free energy of the form
\begin{equation}
  \label{eq:26}
  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
\end{equation}
as expected in general in two-dimensional critical systems \cite{cardy1988finite}. Taking the
derivatives of such expression by $\varepsilon$, we get $f_{0}=f(0)$,
$f_{1}=\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}$,
$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+f_{3}$.

@@

\begin{equation}
  \label{eq:28}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:30}
  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12},
\end{equation}
and
\begin{equation}
  \label{eq:29}
  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}Q(z) dz
    \right].
\end{equation}

@@

\section{Numeric checks}
\label{sec:numeric-checks}
To check our result \eqref{eq:26} numerically, we first need to evaluate the integral in $f_{3}$.
The function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$ is smooth and but some care is required when taking the
limit $z\to 0$ numerically. Evaluating the integral numerically with Mathematica we get
\begin{equation}
  \label{eq:2}
  \int_{0}^{\infty}e^{-z}Q(z)\dz=\int_{0}^{\infty}e^{-z}\frac{\xi(z)-\xi(0)}{z} dz = -0.080842%0.08084228607897521
\end{equation}

@@

Taking the derivatives of $f^{(0)}$ in $\varepsilon$ we get
\begin{multline}
  \label{eq:63}
  \left(\frac{d}{d\varepsilon}\right)^{2} f^{(0)}=\frac{1}{ab\varphi(b-a)} \sum_{n=1}^{\infty}
  \frac{1}{n^{3}}\left[
    \left.\tilde{\chi}''_{\varepsilon\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+
    2n\varphi(b-a)\left.\tilde{\chi}''_{z\varepsilon}\left(n\varepsilon\varphi(b-a),\varepsilon\right)\right|_{\varepsilon=0}+\right.\\\left.
      n^{2}\left(\varphi(b-a)\right)^{2}\tilde{\chi}''_{zz}\left(n\varepsilon\varphi(b-a),\varepsilon\right)  \right]+
    \mathcal{O}(\varepsilon \ln \varepsilon)=\\
    =\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
      \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{z\varepsilon}(0,0)\right]+
    \\
    +\frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon\varphi(b-a)\right)+\mathcal{O}(\varepsilon\ln \varepsilon),
\end{multline}
where the function $\chi(z)$ is the same as in the equation \eqref{eq:39}
\begin{equation}
  \label{eq:64}
  \chi(z)=\frac{z^{2} e^{-z}}{\left(1-e^{-z}\right)^{2}}
\end{equation}
and
\begin{equation}
  \label{eq:65}
  H_{n}=\left(1-e^{-nb\varphi(b-a)}\right) \left(1-e^{-na\varphi(b-a)}\right)
\end{equation}

The last sum in the last line of the equation \eqref{eq:63} is the same as in the section
\ref{sec:gener-other-doma}, thus we can compute it:
\begin{multline}
  \label{eq:66}
  \frac{1}{ab}\sum_{n=1}^{\infty}\frac{H_{n}}{n}\chi''\left(n\varepsilon \varphi(b-a)\right)=
  \frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
    e^{-z}Q(z) \dz+\chi''(0)\sum_{n=1}^{\infty}\frac{H_{n}-1}{n}\right)=\\
  =\frac{1}{ab}\left(\frac{1}{6}\ln \varepsilon +\frac{1}{6}\ln \varphi(b-a)+ \int_{0}^{\infty}
    e^{-z}Q(z) \dz+\frac{1}{6}\ln\left(\frac{\left(1-e^{a\varphi(b-a)}\right)\left(1-e^{a\varphi(b-a)}\right)}{1-e^{(a+b)\varphi(b-a)}}\right)\right),
\end{multline}
where $Q(z)$ was defined in the equation \eqref{eq:85}.

Thus the contribution of $f^{(0)}$ to the asymptotic expansion \eqref{eq:26} consists of the term 
\begin{equation}
  \label{eq:87}
f^{(0)}_{3}=\frac{1}{ab\varphi(b-a)}\left[\sum_{n=1}^{\infty} \frac{1}{n^{3}}
  \tilde{\chi}''_{\varepsilon\varepsilon}(0,0)+2\varphi(b-a)\sum_{n=1}^{\infty}\frac{1}{n^{2}}\tilde{\chi}''_{z\varepsilon}(0,0)\right],
\end{equation}
that is cumbersome but does not depend on $\varepsilon$ and can be computed explicitly and the
expression \eqref{eq:66}, which gives us logarithmic behavior in $\varepsilon$.

Now we need to consider other terms in the expression \eqref{eq:55}. For $f^{+}$ we have
\begin{equation}
  \label{eq:67}
  f^{+}=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n} e^{-n\varepsilon\varphi(b-a)} \varepsilon
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}\varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon)
\end{equation}
The sum over $j$ can be approximated by an integral using Euler-Maclaurin formula as
\begin{equation}
  \label{eq:68}
  \varepsilon\sum_{j=0}^{M-1}\Psi^{+}_{n}(j\varepsilon) = \int_{0}^{a}\Psi^{+}_{n}(x) \dx -
  \frac{\varepsilon}{2}\left(\Psi^{+}_{n}(a)-\Psi^{+}_{n}(0)\right)+
  \frac{\varepsilon^{2}}{12}\left(\Psi^{+'}_{n}(a)-\Psi^{+}_{n}(0)\right)+
  \mathcal{O}\left(\varepsilon^{m}\Psi^{+(m-1)}_{n}\right)
\end{equation}
Since
\begin{equation}
  \label{eq:83}
\Psi_{n}(x)=e^{-nr'(0)x}\left(e^{-n\left(r(x)-xr'(0)\right)}-1\right)=e^{-nxr'(0)}\left(e^{-nx^{2}\zeta(x)}-1\right)  
\end{equation}
we see that $\Psi_{n}(0)=0$ and $\Psi_{n}'(0)=0$.
Than in the limit $n\to\infty$ we have
\begin{equation}
  \label{eq:69}
  \int_{0}^{c}\Psi_{n}(x)
  \dx \xrightarrow[n\to\infty]{}\int_{0}^{c}e^{-nxr'(0)}\left(-nx^{2}\zeta(x)+\dots\right)\sim \frac{1}{n^{2}}
\end{equation}
The derivatives of $\Psi$ behave as $\Psi_{n}^{(m)}(0)\sim n^{m-1}$, since the derivatives should
fall on the bracket in the expression \eqref{eq:83} for the value to be non-zero, and then extra
power of $x$ is produced, which in turn should be differentiated. So the contribution from
$\varepsilon^{m}\Psi_{n}^{(m-1)}(0)$ to $f^{+}$ gives us
\begin{equation}
  \label{eq:70}
  \sum_{n=1}^{\infty} \frac{1}{n} e^{-n\varepsilon\varphi(b-a)}
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} \varepsilon^{m+1}\Psi_{n}^{(m-1)}(0)\sim
  \sum_{n=1}^{\infty} \frac{1}{n^{4}} e^{-n\varepsilon\varphi(b-a)}
  \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}} (\varepsilon n )^{m+1}
\end{equation}
For the second derivative in $\varepsilon$ we thus see that main contribution behaves as
$\sum_{n=1}\frac{1}{n^{2}}e^{-n\varepsilon\varphi(b-a)}
  (n\varepsilon)^{m+1}\xrightarrow[\varepsilon\to 0]{}0$
if $m\geq 3$. For the terms with $m=0,1,2$ we need to
take the limit $\varepsilon\to 0$. Doing so, we obtain
\begin{equation}
  \label{eq:71}
  f^{+}_{3}\equiv\left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{+}\right|_{\varepsilon=0} =
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nbr_{-}'(0)}}{1-e^{-n\varepsilon r_{-}'(0)}}
  \left(\varepsilon\int_{0}^{a} \Psi_{n}^{+}(x) \dx -\varepsilon^{2} \Psi_{n}^{+}(a) +\varepsilon^{3}\Psi^{+'}_{n}(0)\right)\right|_{\varepsilon=0}
\end{equation}
Note that $\frac{\varepsilon}{1-\exp(-n\varepsilon r'_{-}(0))}$ is analytic in $\varepsilon$. 
The derivative can be computed explicitly, but the expression is too long to present it here.

The contribution of $f^{-}$ is computed in exactly the same way:
\begin{equation}
  \label{eq:72}
   f^{-}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2} f^{-}\right|_{\varepsilon=0} =
  \left.\left(\frac{d}{d\varepsilon}\right)^{2}\frac{1}{ab}\sum_{n=1}^{\infty} \frac{1}{n}
  e^{-n\varepsilon\varphi(b-a)} \frac{1-e^{-nar_{+}'(0)}}{1-e^{-n\varepsilon r_{+}'(0)}}
 \left(\varepsilon\int_{0}^{b} \Psi_{n}^{-}(x) \dx -\varepsilon^{2} \Psi_{n}^{-}(a) +\varepsilon^{3}\Psi^{-'}_{n}(0)\right)\right|_{\varepsilon=0}
\end{equation}
At last, we need to consider $f^{\times}$. In this term we can just take a limit $\varepsilon\to 0$
and obtain
\begin{multline}
  \label{eq:73}
   f^{\times}_{3}\equiv \left.\left(\frac{d}{d\varepsilon}\right)^{2}
    f^{\times}\right|_{\varepsilon=0}=\left.\frac{1}{ab}\sum_{n=1}^{\infty}\frac{1}{n}
  \left(\frac{d}{d\varepsilon^{2}}\right)^{2}\left(\int_{0}^{b}\Psi^{-}_{n}(x)\dx
    -\frac{\varepsilon}{2}\Psi^{-}_{n}(b)+\frac{\varepsilon^{2}}{12}\Psi^{-'}_{n}(b)\right)\cdot\right.\\
\cdot\left.\left(\int_{0}^{a}\Psi^{+}_{n}(x)\dx-\frac{\varepsilon}{2}\Psi^{+}_{n}(a)+
    \frac{\varepsilon^{2}}{12}\Psi^{+}_{n}(a)\right)\right|_{\varepsilon=0} 
\end{multline}
Again, this expression is easily computed explicitly, but is too cumbersome to present it here.

At last we can write the asymptotic expansion coefficients in the present case:
\begin{equation}
  \label{eq:84}
  f_{0}= -\frac{1}{ab}\int_{0}^{b}\int_{0}^{a}\ln
  \left(1-e^{-\int_{-y}^{z}\varphi\left(b-a+x\right)\dx} \right)\dz\dy
\end{equation}
\begin{equation}
  \label{eq:88}
  f_{1}=0
\end{equation}
\begin{equation}
  \label{eq:89}
  f_{2}=\frac{1}{ab}\frac{1}{12}    
\end{equation}
\begin{multline}
  \label{eq:90}
  f_{3}=f^{(0)}_{3}+f^{+}_{3}+f^{-}_{3}+f^{\times}_{3}+
  \frac{1}{ab}\frac{1}{12}\ln\left(\frac{\varphi(b-a)\left(1-e^{a\varphi(b-a)}\right)\left(1-e^{a\varphi(b-a)}\right)}{1-e^{(a+b)\varphi(b-a)}}\right)+\\
  +\frac{1}{ab}\left(\frac{1}{8} +\frac{1}{2} \int_{0}^{\infty}
    e^{-z}q(z) \dz\right),
\end{multline}
Here in the first line we have the contributions that depend on the choice of the weight function
$\varphi$ and in the second line -- the universal contribution that appears in the case
$\varphi\equiv 1$ and in the box of finite height.

\subsection{Numerical checks}
\label{sec:numerical-checks-nonuniform}
Here we present results of comparison of numerical values of the expansion coefficients
$f_{0},f_{1},f_{2},f_{3}$ that were obtained from analytical formulas
\eqref{eq:84},\eqref{eq:88},\eqref{eq:89},\eqref{eq:90} using Mathematica computer algebra system
with the results of fitting exact numeric values of free energy for $\frac{1}{\varepsilon}=2\dots
200$
by the formula $f=f_{0}+
f_{1}\varepsilon+
f_{2}\varepsilon^{2}\ln\varepsilon+f_{3}\varepsilon^{2}+f_{4}\varepsilon^{3}+f_{5}\varepsilon^{4}$.

In the table we present results for various functions $\varphi(z)$ and values of $a,b$.
\begin{table}[htpb]
\begin{center}
\begin{tabular}{c|cccccc}
  & $\varphi(z)$ & $a,b$ & $f_{0}$ &  $f_{1}$ &  $12ab f_{2}$ &  $f_{3}$ \\
 \hline
 analytic & $\frac{1}{3}(2+\cos(z))$ & 1,3 & $0.472206688$ & $0$ & $1$&$-0.043883000$\\
 numeric & $\frac{1}{3}(2+\cos(z))$ & 1,3 &  $0.472206693$ & $0.000000730$ & $1.000730689$&$-0.043827958$\\
  \hline
 analytic & $\frac{1}{3}(2+\cos(z))$ & 2,3 & $0.235922467$ & $0$ & $1$&$-0.030398000$\\
 numeric & $\frac{1}{3}(2+\cos(z))$ & 2,3 &  $0.235922467$ & $0.000000044$ & $1.000088528$&$-0.030394694$\\
\hline                                                
 analytic & $a+z/2$ & 1,3 & $0.097288596$ & $0$ & $1$&$-0.033688300$\\
 numeric & $a+z/2$ & 1,3 &  $0.097288593$ & $0.000000848$ & $1.000848267$&$-0.033624441$\\
\hline                                                
 analytic & $a+z/2$ & 2,3 & $0.032804447$ & $0$ & $1$&$-0.015094000$\\
 numeric & $a+z/2$ & 2,3 &  $0.032804447$ & $-0.000000002$ & $0.999996808$&$-0.015094162$\\
\end{tabular}
\caption{Values of the fitted parameters and analytically computed expansion coefficients for
  various weight functions $\varphi$ and values of $a,b$.
}
\label{tttt1}
\end{center}
\end{table}

We see very good coincidence between values, obtained numerically and analytically.

%%  
%%  If we assume that $\varphi(b-a)\neq 0$, we can again obtain function $\chi(z)$:
%%  \begin{multline}
%%    \label{eq:24}
%%     f=\frac{1}{ab}\sum_{n=1}^{\infty}\frac{\chi\left(n\varepsilon\varphi(b-a)\right)}{n^{3}}\left(1-e^{-n\varepsilon
%%         \varphi(b-a)}\right)^{2}\frac{1}{\varphi^{2}(b-a)}\cdot\\
%%     \cdot\left(1+\sum_{i=1}^{N-1}
%%       e^{-n\varepsilon\sum_{k=1}^{i}\varphi\left(b-a-k\varepsilon\right)}\right)
%%     \left(1+\sum_{j=1}^{M-1}e^{-n\varepsilon\sum_{l=1}^{j}\varphi\left(b-a+l\varepsilon\right)}\right)  
%%  \end{multline}
%%

@@

In further work we will study the connection of the expansion coefficients with the spectral
properties of Dirac operator on the non-frozen domain and study the universality of our results. We
will also further discuss the description of the model by boundary conformal field theory.

\section*{Acknowledgments}
\label{sec:acknowledgements}
We are grateful to professor Nikolai Reshetikhin for his attention to this work. We thank Pavel Belov
for useful discussions and general support.

We thank the organizers and participants of the conference MQFT-2018 for the opportunity
to present our results and useful discussions.
